A Toolbox for Manipulating and Assessing Color Palettes for Statistical Graphics

### 2019-03-18 pkg/colorspace/paper/Toolbox/slides.Rnw
arxiv paper
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/colorspace@488 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

Ihaka R, Murrell P, Hornik K, Fisher JC, Stauffer R, Wilke CO, McWhite CD, Zeileis A (2019).
  \emph{colorspace: A Toolbox for Manipulating and Assessing Colors and Palettes.}
  \url{http://colorspace.R-Forge.R-project.org/}

>>>>

Zeileis A, Fisher JC, Hornik K, Ihaka R, McWhite CD, Murrell P, Stauffer R, Wilke CO (2019).
  \dquote{colorspace: A Toolbox for Manipulating and Assessing Colors and Palettes.}
  arXiv:1903.06490, arXiv.org E-Print Archive.
  \url{http://arxiv.org/abs/1903.06490}
